Random Walks across Social Networks: The Markovian Movement of a Stochastic Soccerball

### 2020-07-24 rmd/Preprocessing_Python.Rmd
done almost

```{python}
for league in national_leagues:
    preprocess(league)
```

```{python}
# Correct data for De Bruyne's goal vs Chelsea (not an inaccurate pass!)

england_events = pd.read_csv('../data/processed/England.csv')

england_events.at[102730,'eventName'] = 'Shot'
england_events.at[102730,'subEventName'] = 'Goal'
england_events.at[102730,'accurate'] = 1
england_events.at[102730,'to_team'] = 'Away Goal'
england_events.at[102730,'target'] = 'Goal'
england_events.at[102730,'target_y'] = 50

england_events.to_csv('../data/processed/England.csv',index=False)
```

>>>>

```{python}
for league in national_leagues:
    preprocess(league)
```
``

### 2020-07-24 rmd/SocialNetworkAnalysis_R.Rmd
done almost

# Executive Summary

# Introduction

```{r}
library(plyr) # data manipulation @HWickham2009
library(dplyr) # data manipulation @HWickham@2017
library(knitr) # dynamic report generation @YXie2012
library(igraph) # for graph/network analysis @GCsardiTNepusz2006
library(ggraph) # graph visualization in the style of ggplot @TPederson2016a
library(netrankr) # network centrality @DSchoch2015
library(ggplot2) # for plotting visualizations @HWickham2007
library(ggforce) # adds functionality to ggplot2, eg. geom_circle @TPederson2016b
library(ggrepel) # adds 'repellent' non-overlapping labels to ggplot @KSlowikowski2016
library(pheatmap) # prettier heat maps
library(RColorBrewer) # color palettes
library(docstring) # allows ?help to display function descriptions analogous to Pythonic docstrings
```

@@

# Data

```{r}
events <- LoadAndScaleData('England')
```

```{r}
events[1:10,]
```

```{r}
LeagueResults <- function(league){
    #' Calculate results and table for given national league.

    home_score <- matrix(0, nrow=length(teams), ncol=length(teams))
    colnames(home_score) <- teams
    rownames(home_score) <- teams

    away_score <- home_score

        home_score[home_team, away_team] <- home_goals
        away_score[home_team, away_team] <- away_goals

```{r}
prem <- LeagueResults(events)
```

```{r}
pl <- as.data.frame(prem)
```

```{r}
pl['Team'] <- rownames(pl)
```

```{r}
pl2 <- as.data.frame(pl[,c(10,2:9)])
```

```{r}
rownames(pl2) <- c()
```

```{r}
pl2[1:5,]
```

```{r}
prem[1:5,]
```

```{r}
NationalResults <- function(nation) {

    data <- LoadAndScaleData(nation)
    results <- LeagueResults(data)
    return(results)
}

```{r}

```{r}
correct_res <- read.csv('../data/league_results/England17-18.csv')
```

```{r}
correct_res
```

```{r}
france <- NationalResults('France')
germany <- NationalResults('Germany')
italy <- NationalResults('Italy')
spain <- NationalResults('Spain')
```

```{r}
premiership <- NationalResults('England')
```

@@

    # draw pitch
    p <- DrawPitch(theme='grey', arrow=direction_of_play) + 
        geom_point(data = game_events, 
               aes(location_x , location_y, fill=eventName, shape=eventName), pch=21, alpha=0.6, size=2 ) + 
        geom_point(data=game_events[game_events$subEventName=='Goal',], 
                   aes(location_x, location_y), shape=13, size=5) +
        geom_label_repel(data=game_events[game_events$subEventName=='Goal',], 
                         aes(location_x, location_y, label = paste0(source,'(',matchPeriod,' ',time,')')), label.padding=0.1, size=2.3, alpha=1) +
        theme(legend.direction='horizontal', legend.position=c(0.5,0)) +
        scale_fill_manual(values=c("red", "black", 'white', "yellow", 'blue'), name='Event Type') +
        ggtitle(paste('Event Map:', team_name,'playing',home_or_away,'versus',opposition,'(',team_score,'-',opposition_score,')'))

@@

```{r}
#away vs Crystal Palace
match_id <- '2500032'
```

```{r}
# vs man city
match_id <- '2499943'
```

```{r}
ShowMatchEvents(events, match_id, home_or_away='Home')
ShowMatchEvents(events, match_id, home_or_away='Away', flip=T)
```

@@

    # draw pitch
    p <- DrawPitch(theme='grass', arrow=direction_of_play) + 
        geom_segment(data=na.exclude(passes), 
                     aes(x=location_x, y=location_y, xend=target_x, yend=target_y, color=subEventName), 
                     alpha=0.6, arrow = arrow(length = unit(0.1,"cm"))) +
        geom_label_repel(data=game[game$subEventName=='Goal',], 
                     aes(location_x, location_y, label = paste0(source,'(',matchPeriod,' ',time,')')), label.padding=0.1, size=2.3, alpha=1) + 
        geom_segment(data=na.exclude(shots), 
                 aes(x=location_x, y=location_y, xend=target_x, yend=target_y, color=subEventName), 
                 alpha=0.7, arrow = arrow(length = unit(0.1,"cm"))) +
        theme(legend.position=c(0.5,-0.01), legend.direction='horizontal',
              legend.background=element_rect(fill='#008000', linetype='solid')) +
        scale_color_manual(values=c("red", "black", 'blue', 'orange', "yellow", 'grey', 'purple', 'white','brown'), name='Pass Type') +
        ggtitle(paste('Pass Map:',team_name,'playing',home_or_away,'versus',opposition,'(',team_score,'-',opposition_score,')'))

@@

```{r}
ShowPassesAndShots(events, match_id, home_or_away='Home')
ShowPassesAndShots(events, match_id, home_or_away='Away', flip=T)
```

# Methodology

@@

    return (DrawPitch() +
        geom_segment(data=team[team$passcount>=lower_threshold,], size=1, colour=team_colour,
                     aes(x=source_x, y=source_y, xend=x_mean, yend=y_mean, alpha=passcount)) +
        geom_segment(data=team[team$passcount>=high_threshold,], size=1.5, colour='black',
                     aes(x=source_x, y=source_y, xend=x_mean, yend=y_mean, alpha=passcount)) +
        geom_label_repel(data = mean_positions[mean_positions$team==team_name,], 
                         aes(x_mean, y_mean, label = target), label.padding=0.1, size=2.3, alpha=1) +
        geom_point(data=team, aes(x_mean, y_mean,), fill=team_colour, colour='black', pch=21, size=3) +
        ggtitle(paste('Passing Network:',team_name,'playing',home_or_away,'versus',opposition,'(',team_score,'-',opposition_score,')')) +
        theme(legend.position=c(0.5,0.07), legend.direction='horizontal'))

```{r}
PassNetwork(events, match_id, team_colour='red')
PassNetwork(events, match_id, team_colour='blue', home_or_away='Away', flip=T)
```

```{r}
2499943
```

```{r}

@@

@@

    max_steps <- 10000
#     transition_matrix <- TransitionMatrix(GameGraph(events, match_id))
    hitting_times <- rep(0,(ncol(transition_matrix)-2))

@@

        state_probabilities <- matrix(NA,nrow=max_steps+1,ncol=ncol(transition_matrix),
                                      dimnames=list(0:max_steps,(ncol(transition_matrix)-1):0))
        vector <- rep(0,ncol(transition_matrix))

@@

```{r}
SeasonAdjacencyMatrix <- function(events, team) {

@@

```{r}
MarkovExpectedGoals <- function(events, season_adjacency_matrix) {

    season_graph <- graph_from_adjacency_matrix(season_adjacency_matrix)
    season_transition <- TransitionMatrix(season_graph)
    seasonXST <- ExpectedScoringTime(season_transition)
    seasonMXG <- 1/seasonXST
    normalize <- seasonMXG/(mean(seasonMXG))
    avg_events_per_game <- nrow(events)/380
    scale <- normalize * avg_events_per_game - avg_events_per_game
    sorted <- sort(scale, decreasing=T)

    return(sorted)
}
```

```{r}
GoalProbabilities <- function(season_adjacency_matrix) {

    season_graph <- graph_from_adjacency_matrix(season_adjacency_matrix)
    season_transition <- TransitionMatrix(season_graph)
    goal_probs <- sort(season_transition[,'Goal'],T)[2:nrow(season_transition)] * 100

    return(goal_probs)
}
```

```{r}
leagueMXG <- function(events){

    all_mXG <- c()
    teams <- unique(events$team)

    for (team in teams){

        season_adjacency_matrix <- SeasonAdjacencyMatrix(events, team)
        mXG <- MarkovExpectedGoals(events, season_adjacency_matrix)

        all_mXG <- append(all_mXG, mXG)

    return(all_mXG)
}
```

```{r}
mXG <- c()
leagues = c('England','France','Germany','Italy','Spain')
for (league in leagues){
    events <- LoadAndScaleData(league)
    mXG <- append(mXG, leagueMXG(events))
}
```

```{r}
sort(mXG,T)
```

```{r}

@@

```{r}

@@

```{r}
g <- GameGraph(events, match_id, home_or_away='Home')
```

```{r}
MatrixHeatMap <- function(matrix, number_format='%.d', title='Matrix Heatmap'){
    #' Show Matrix as HeatMap

    hm <- pheatmap(matrix,color=brewer.pal(15,'YlGnBu'),cluster_rows=F,cluster_cols=F,legend=F,
                    display_numbers=T,number_format=number_format,fontsize_number=9,angle_col='315',
                    main=title)

```{r}
MatrixHeatMap(
    AdjacencyMatrix(g)[1:11,1:11]

)
```

```{r}
MatrixHeatMap(
    AdjacencyMatrix(
        GameGraph(events, match_id, home_or_away='Away'))[1:11,1:11]
)
```

```{r}
MatrixHeatMap(
    TransitionMatrix(
        GameGraph(events, match_id, home_or_away='Home')), 
    number_format='%.2f',
    title=''
)
```

```{r}
MatrixHeatMap(
    TransitionMatrix(
        GameGraph(events, match_id, home_or_away='Away')), 
    number_format='%.2f',
    title=''
)
```

    return(kable(df))
}
```

```{r}
sequence <- '2500032-91-Liv-0'
```

```{r}
TabulateSequence(events, sequence)
```

    p <- DrawPitch(theme='grass') + 
        geom_label_repel(data = data, aes(location_x, location_y, label = paste(source,time)), label.padding=0.1, size=2.3, alpha=1) +
        geom_curve(data = data, aes(x = location_x, xend = target_x, y = location_y, yend = target_y*.99, col = X), 
                   show.legend=FALSE, size=1, alpha = 1) +
        geom_point(data = data, aes(location_x , location_y, shape=eventName), size=2) + 
        ggtitle(paste0(nrow(data),'-part ', unique(data$team)[1], ' Possession Sequence ending with ', 
                       data[nrow(data),]$subEventName, ' by ', data[nrow(data),]$source))  +
        theme(legend.position=c(0.5,0.08), legend.direction='horizontal', legend.title=element_blank())

```{r}
SequenceOnPitch(events, sequence)
```

youtube clip
<img src="../figures/youtube_clip.gif" width='700'>

@@

```{r}
g <- SequenceGraph(events, sequence)
```

```{r}
VisualizeGraph(g)
```

```{r}
GetGraphMetrics <- function(possession_graph) {
    #' Return basic metrics for given Graph

    g <- possession_graph
    path_metrics <- c(g$id, g$team, length(V(g)), length(E(g)), 
                      diameter(g), mean_distance(g), edge_density(g, loops=T), 
                      girth(g)$girth, transitivity(g), authority_score(g)$value, hub_score(g)$value)
    names(path_metrics) <- c('Label', 'Team', 'Nodes', 'Edges', 'Diameter', 'Mean_Distance', 
                             'Edge_Density', 'Girth', 'Transitivity', 'Authority_Score', 'Hub_Score')

    return(path_metrics)
}
```

```{r}
GetNodeMetrics <- function(possession_graph) {
    #' Return metrics for each Node of given Graph

    g <- possession_graph
    df <- data.frame(page_rank(g)$vector)
    names(df) <- 'pagerank'
    df$in_degree <- degree(g, mode='in')
    df$out_degree <- degree(g, mode='out')
    df$eccentricity <- eccentricity(g)
    df$closeness <- closeness(g)
    df$betweenness <- betweenness(g)
    df$norm_betweenness <- betweenness(g, normalized=T)
    df$alpha_centrality <- alpha_centrality(g)
    df$power_centrality <- power_centrality(g)
    df$eigen_centrality <- eigen_centrality(g)$vector
    df$authority <- authority_score(g)$vector
    df$hub <- hub_score(g)$vector

```{r}
GetEdgeMetrics <- function(possession_graph) {
    #' Return metrics for each Edge of given Graph

    g <- possession_graph
    df <- data.frame(as_edgelist(g))
    names(df) <- c('Source','Target')
    df$sequence <- 1:length(E(g))
    df$edge_betweenness <- edge_betweenness(g)

```{r}
GetGraphMetrics(g)
```

```{r}
GetNodeMetrics(match_graph)
```

```{r}
GetEdgeMetrics(g)
```

```{r}
sequence2 <- '2499858-18-Liv-5'
```

```{r}
TabulateSequence(sequence2)
```

```{r}
SequenceOnPitch(sequence2)
```

<img src='../figures/mane_vs_stoke.gif'>

```{r}
g2 <- SequenceGraph(sequence2)
VisualizeGraph(g2)
```

```{r}
GetGraphMetrics(g2)
```

```{r}
sequence3 <-  '2499889-18-Liv-0'
```

```{r}
SequenceOnPitch(sequence3)
```

```{r}
g3 <- SequenceGraph(sequence3)
VisualizeGraph(g3)
```

```{r}
GetGraphMetrics(g3)
```

<img src="../figures/youtube_clip2.gif">

```{r}

>>>>

```{r}
library(plyr) # data manipulation 
library(dplyr) # data manipulation
library(igraph) # for graph/network analysis 
library(ggraph) # graph visualization in the style of ggplot
library(netrankr) # network centrality
library(ggplot2) # for plotting visualizations
library(ggforce) # adds functionality to ggplot2, eg. geom_circle
library(ggrepel) # adds 'repellent' non-overlapping labels to ggplot
library(pheatmap) # prettier heat maps
library(RColorBrewer) # color palettes
library(docstring) # allows ?help to display function descriptions analogous to Pythonic docstrings
```

```{r}
LeagueResults <- function(league){
    #' Test data integrity by calculating results and table for given national league.

@@

@@

    # draw pitch
    p <- DrawPitch(theme='grey', arrow=direction_of_play) + 
        geom_point(data = game_events, 
               aes(location_x , location_y, fill=eventName, shape=eventName), pch=21, alpha=1, size=2 ) + 
        geom_point(data=game_events[game_events$subEventName=='Goal',], 
                   aes(location_x, location_y), shape=13, size=5) +
#         geom_label_repel(data=game_events[game_events$subEventName=='Goal',], 
#                          aes(location_x, location_y, label = paste0(source,'(',matchPeriod,' ',time,')')), label.padding=0.1, size=2.3, alpha=1) +
        theme(legend.direction='horizontal', legend.position=c(0.5,0)) +
        scale_fill_manual(values=c("red", "black", 'white', "yellow", 'blue'), name='Event Type') +
        ggtitle(paste('Event Map:', team_name,home_or_away,'versus',opposition,'(',team_score,'-',opposition_score,')'))

    p$figname <- paste0('EventMap',home_or_away)

@@

@@

    # draw pitch
    p <- DrawPitch(theme='grass', arrow=direction_of_play) + 
        geom_segment(data=na.exclude(passes), 
                     aes(x=location_x, y=location_y, xend=target_x, yend=target_y, color=subEventName), 
                     alpha=1, arrow = arrow(length = unit(0.1,"cm"))) +
#         geom_label_repel(data=game[game$subEventName=='Goal',], 
#                      aes(location_x, location_y, label = paste0(source,'(',matchPeriod,' ',time,')')), label.padding=0.1, size=2.3, alpha=1) + 
        geom_segment(data=na.exclude(shots), 
                 aes(x=location_x, y=location_y, xend=target_x, yend=target_y, color=subEventName), 
                 alpha=1, arrow = arrow(length = unit(0.1,"cm"))) +
        theme(legend.position=c(0.5,-0.01), legend.direction='horizontal',
              legend.background=element_rect(fill='#008000', linetype='solid')) +
        scale_color_manual(values=c("red", "black", 'blue', 'orange', "yellow", 'grey', 'purple', 'white','brown'), name='Pass Type') +
        ggtitle(paste('Pass Map:',team_name,home_or_away,'versus',opposition,'(',team_score,'-',opposition_score,')'))

    p$figname <- paste0('PassMap',home_or_away)

@@

    p <- DrawPitch(theme='grass') + 
        geom_label_repel(data = data, 
                         aes(location_x, location_y, label = paste(source,time)), 
                         label.padding=0.1, size=2.3, alpha=1) +
        geom_curve(data = data, 
                   aes(x = location_x, xend = target_x, 
                       y = location_y, yend = target_y*.99, col = X), 
                   show.legend=FALSE, size=1, alpha = 1) +
        geom_point(data = data, 
                   aes(location_x , location_y, shape=eventName), size=2) + 
        ggtitle(paste0(nrow(data),'-part ', unique(data$team)[1], 
                       ' Possession Sequence \nending with ', 
                       data[nrow(data),]$subEventName, ' by ', 
                       data[nrow(data),]$source))  +
        theme(legend.position=c(0.5,0.08), 
              legend.direction='horizontal', 
              legend.title=element_blank())

@@

    p <- (DrawPitch() +
        geom_segment(data=team[team$passcount>=lower_threshold,], 
                     size=1, colour=team_colour,
                     aes(x=source_x, y=source_y, 
                         xend=x_mean, yend=y_mean, alpha=passcount)) +
        geom_segment(data=team[team$passcount>=high_threshold,], 
                     size=1.5, colour='black',
                     aes(x=source_x, y=source_y, 
                         xend=x_mean, yend=y_mean, alpha=passcount)) +
        geom_label_repel(data = mean_positions[mean_positions$team==team_name,], 
                         aes(x_mean, y_mean, label = target), 
                         label.padding=0.5, size=4, alpha=0.8) +
        geom_point(data=team, aes(x_mean, y_mean,), 
                   fill=team_colour, colour='black', pch=21, size=3) +
        ggtitle(paste('Passing Network:',team_name,home_or_away,
                      'versus',opposition,'(',team_score,'-',opposition_score,')')) +
        theme(legend.position=c(0.5,0.07), legend.direction='horizontal'))

    p$figname <- paste0('PassingNetwork',home_or_away)

@@

```{r}
MatrixHeatMap <- function(matrix, color, number_format, title){
    #' Show Matrix as HeatMap

    hm <- pheatmap(matrix,color=color,
                   cluster_rows=F,cluster_cols=F,legend=F,
                    display_numbers=T,number_format=number_format,
                   fontsize_number=9,angle_col='315',
                    main=title)

@@

    max_steps <- 10000
    hitting_times <- rep(0,(ncol(transition_matrix)-2))

@@

        state_probabilities <- matrix(NA,
                                      nrow=max_steps+1,
                                      ncol=ncol(transition_matrix),
                        dimnames=list(0:max_steps,(ncol(transition_matrix)-1):0))
        vector <- rep(0,ncol(transition_matrix))

@@

```{r}
SeasonAdjacencyMatrix <- function(events, team) {
    #' Return Adjacency Matrix for Team's full season.

@@

```{r}
MarkovExpectedGoals <- function(events, season_adjacency_matrix) {
    #' Calculate MXG for each player from team's Season Adjacency Matrix.

    season_graph <- graph_from_adjacency_matrix(season_adjacency_matrix)
    season_transition <- TransitionMatrix(season_graph)
    seasonXST <- ExpectedScoringTime(season_transition)
    seasonMXG <- 1/seasonXST
    stdize <- seasonMXG/(mean(seasonMXG))
    avg_events_per_game <- sum(season_adjacency_matrix)/38
    scale <- stdize * avg_events_per_game - avg_events_per_game

    return(scale)
}
```

```{r}
MXGTable <- function(events, team){
    #' Return dataframe with Degree, Loops, Goals, and MXG for each player in team.

    Team <- team
    m <- SeasonAdjacencyMatrix(events,Team)
    Degree <- rowSums(m)[1:(nrow(m)-2)]
    Loops <- diag(m)[1:(nrow(m)-2)]
    Goals <- m[,ncol(m)][1:(nrow(m)-2)]
    Player <- rownames(m)[1:(nrow(m)-2)]
    MXG <- MarkovExpectedGoals(events, m)[1:(nrow(m)-2)]
    df <- data.frame(Player, Team, MXG, Goals, Loops, Degree)   
    rownames(df) <- c()

    return(df)
}

@@

```{r}
CalculateMXG <- function() {
    #' Get MXG and other stats for each player in all leagues.

    mxgtable_df <- data.frame(Player = character(),
                    Team = character(),
                    MXG = double(),
                    Goals = integer(),
                    Loops = integer(),
                    Degree = integer())

    leagues = c('England','France','Germany','Italy','Spain')
    for (league in leagues){
        events <- LoadAndScaleData(league)
        for (team in unique(events$team)){
            mxgtable_df <- rbind(mxgtable_df, MXGTable(events,team))

        }
    }

    write.csv(mxgtable_df[order(-mxgtable_df[,'MXG']),], file='../tables/MXG.csv', row.names=F)

```{r}
TallyEventTypes <- function(events, eventType=F){
    #' Return dataframe with tallies for specified type.

    if (eventType!=F){
        events <- events[events$eventName==eventType,]
        df <- data.frame(table(events$subEventName))
        df <- df[df$Freq>0,]
    } else {
        df <- data.frame(table(events$eventName))
    }

    df <- df[order(-df$Freq),]
    colnames(df)[1:2] <- c('Description','Frequency')

    df$Description <- as.character(df$Description)

    total <- sum(df$Frequency)
    df[nrow(df)+1,] <- c('**Total**',total)
    df$Frequency <- as.numeric(df$Frequency)

    df$Pct <- df$Frequency / total * 100
    rownames(df) <- c()
    colnames(df)[3] <- '%'

    df[,3] <- formatC(signif(df[,3],digits=3), digits=3,format="fg", flag="#")

    df[,'Frequency (%)'] <- paste0(as.character(
                            prettyNum(df$Frequency, big.mark=",", scientific=F)),
                           ' (', as.character(df[,3]),'%)')

    df <- df[,c(1,4)]

```{r}
ExploratoryTallies <- function(){
    #' Get exploratory tallies.

    events <- LoadAndScaleData('England')

    leagues = c('England','France','Germany','Italy','Spain')
    for (league in leagues[2:5]){
        events <- rbind(events, LoadAndScaleData(league))
    }

    types <- TallyEventTypes(events)
    passes <- TallyEventTypes(events,'Pass')
    shots <- TallyEventTypes(events,'Shot')

    write.csv(types,'../tables/EventTypeTally.csv',row.names=F)
    write.csv(passes,'../tables/PassTally.csv',row.names=F)
    write.csv(shots,'../tables/ShotTally.csv',row.names=F)

```{r}
SavePairedFigures <- function(league, match_id){
    #' Generate and Save Paired Figures.

    events <- LoadAndScaleData(league)

    EventMapHome <- ShowMatchEvents(events, match_id)
    EventMapAway <- ShowMatchEvents(events, match_id, home_or_away='Away', flip=T)

    PassMapHome <- ShowPassesAndShots(events, match_id)
    PassMapAway <- ShowPassesAndShots(events, match_id, home_or_away='Away', flip=T)

    PassingNetworkHome <- PassNetwork(events, match_id, team_colour='blue')
    PassingNetworkAway <- PassNetwork(events, match_id, home_or_away='Away', 
                                      team_colour='red',flip=T)

    pairedFigures <- list(EventMapHome, EventMapAway,
                      PassMapHome, PassMapAway,
                      PassingNetworkHome, PassingNetworkAway)

    for (fig in pairedFigures){
        png(filename=paste0('../figures/',fig$figname,'.png'),
            width=800, 
            height=650,
            units='px',
           pointsize=4,
           res=140)
        print(fig)
        dev.off()

    }   
}

@@

```{r}
CountSequences <- function(events) {
    #' Count Possession Sequences and return DataFrame.

    poss_seqs <- data.frame(table(events$possession))
    df_psq <- data.frame(table(poss_seqs$Freq))
    goals_seqs <- events[events$subEventName == 'Goal',]$possession
    goals_seqs_events <- events[events$possession %in% goals_seqs,]
    df_gpsq0 <- data.frame(table(goals_seqs_events$possession))
    df_gpsq <- df_gpsq0[df_gpsq$Freq>0,]
    df_g <- data.frame(table(df_gpsq$Freq))

    m <- rbind(1:10, df_psq$Freq[1:10], df_g$Freq[1:10])
    mdf <- data.frame(m)
    rownames(mdf) <- c('Sequence Length', 'Frequency', 'Goal Scoring')

    total_goals <- sum(df_g$Freq)
    total_seqs <- sum(df_psq$Freq)
    final <- c('**Total**', total_seqs, total_goals)
    mdf <- cbind(mdf,final)
    colnames(mdf) <- c()

    df <- t(mdf)
    df[,2] <- prettyNum(df[,2], big.mark=",", scientific=F)
    df[,3] <- prettyNum(df[,3], big.mark=",", scientific=F)
    return(df)
}
```

```{r}
PossessionSequence <- function(league, sequence){
    #' Generate Figures and Table for given Possession Sequence.

    events <- LoadAndScaleData(league)
    write.csv(TabulateSequence(events, sequence),'../tables/PossessionSequence.csv',row.names=F)
    png(filename=paste0('../figures/PossessionSequence.png'),
        width=800, 
        height=600,
        units='px',
       pointsize=12,
       res=140)
    print(SequenceOnPitch(events, sequence))
    dev.off()

    g <- SequenceGraph(events, sequence)
    png(filename=paste0('../figures/PossessionGraph.png'),
        width=800, 
        height=600,
        units='px',
       pointsize=12,
       res=140)
    print(VisualizeGraph(g))
    dev.off()
}
```

```{r}
Top20MXG <- function(){
    #' Save CSV with top 20 players by MXG score.

    d <- read.csv('../tables/MXG.csv')
    top <- d[d$Degree>1000,]
    rownames(top) <- c()
    top['Loops/Degree'] <- top$Loops/top$Degree
    top['Goals/Degree'] <- top$Goals/(top$Degree)
    t <- top[c('Player','Team','Degree','Goals',
               'Goals/Degree','Loops','Loops/Degree','MXG')]
    write.csv(t[1:20,], '../tables/2.csv',row.names=F)
}

```{r}
SaveMatrixHeatmaps <- function(league, match_id, team_name){
    #' Save Heatmaps for Adjacency and Transition Matrices.

    events <- LoadAndScaleData(league)
    g <- GameGraph(events, match_id, team_name)
    adj_m <- AdjacencyMatrix(g)
    tr_m <- TransitionMatrix(g)

    matrix_cols <- c('darkgrey',colorRampPalette(c('white','red'))(35))
    adj_m_hm <- MatrixHeatMap(adj_m[1:11,1:11], color=matrix_cols, number_format='%.0f',
                  title=paste('Adjacency Matrix for',g$team,'(Starting XI)\n',
                              g$status,'vs.',g$opposition))
    adj_m_hm$type <- 'Adjacency'

    tr_m_hm <- MatrixHeatMap(tr_m, color=matrix_cols[2:36], number_format='%.2f',
                  title=paste('Transition Matrix for',g$team,g$status,'vs.',g$opposition))
    tr_m_hm$type <- 'Transition'

    hm_vec <- list(adj_m_hm, tr_m_hm)

    for (hm in hm_vec){
        png(filename=paste0('../figures/',hm$type,'MatrixAway.png'),
            width=1600, 
            height=1600,
            units='px',
           pointsize=12,
           res=240)

        print(hm)

        dev.off()   
    }

@@

```{r}
GenerateTablesAndFigures <- function(league, match_id, possession_seq, team){
    #' Generate Tables and Figures for Paper.

    ExploratoryTallies()
    SavePairedFigures(league, match_id)
    PossessionSequence(league, possession_seq)
    SaveMatrixHeatmaps(league, match_id, team)
    CalculateMXG()
    Top20MXG()
}
```

```{r}
GenerateTablesAndFigures('England','2500032','2500032-91-Liv-0','Liverpool')
```
